The \dealii{} Library, Version 9.2

### 2020-05-30 9.2/paper.tex
Add author: JPP

\hypersetup{
  pdfauthor={
     Daniel Arndt,
     Wolfgang Bangerth,
     Bruno Blais,
     Thomas C. Clevenger,
%     Denis Davydov,
    Marc Fehling,
%     Daniel Garcia-Sanchez,
    Alexander V. Grayver,
%     Graham Harper,
    Timo Heister,
    Luca Heltai,
    Martin Kronbichler,
    Peter Munch,
%     Ross Maguire Kynch,
    Matthias Maier,
%     Jean-Paul Pelteret,
    Reza Rastak,
    Bruno Turcksin,
    David Wells
    Zhuoran Wang,
  },
  pdftitle={The deal.II Library, Version 9.2, 2020},
}

@@

%
% \author[4]{Jean-Paul~Pelteret}
%
 \author[11]{Reza Rastak}
 \affil[11]{Department of Civil and Environmental Engineering,
   Stanford University,
   Stanford, CA 94305, USA.
   {\texttt{rastak@stanford.edu}}}

 \author[**12]{Ignacio Tomas}
 \affil[12]{Sandia National Laboratories, Org 1442,
 P.O. Box 5800, MS 1320, Albuquerque, NM, 87185-1320,
   \texttt{itomas@sandia.gov}}

\author[*1]{Bruno~Turcksin}
%
\author[13]{David Wells}
\affil[13]{Department of Mathematics, University of North Carolina,
  Chapel Hill, NC 27516, USA.
  {\texttt{drwells@email.unc.edu}}}

\author[14]{Zhuoran Wang}
\affil[14]{Department of Mathematics, Colorado State University, Fort Collins,
          CO 80523-1874, USA.
{\texttt{zhrwang@math.colostate.edu}}}
\renewcommand{\labelitemi}{--}

>>>>

\hypersetup{
  pdfauthor={
     Daniel Arndt,
     Wolfgang Bangerth,
     Bruno Blais,
     Thomas C. Clevenger,
%     Denis Davydov,
    Marc Fehling,
%     Daniel Garcia-Sanchez,
    Alexander V. Grayver,
%     Graham Harper,
    Timo Heister,
    Luca Heltai,
    Martin Kronbichler,
    Peter Munch,
%     Ross Maguire Kynch,
    Matthias Maier,
    Jean-Paul Pelteret,
    Reza Rastak,
    Bruno Turcksin,
    David Wells
    Zhuoran Wang,
  },
  pdftitle={The deal.II Library, Version 9.2, 2020},
}

@@

\author[11]{Jean-Paul~Pelteret}
\affil[11]{Independent researcher.
{\texttt{jppelteret@gmail.com}}}

 \author[12]{Reza Rastak}
 \affil[12]{Department of Civil and Environmental Engineering,
   Stanford University,
   Stanford, CA 94305, USA.
   {\texttt{rastak@stanford.edu}}}

 \author[**13]{Ignacio Tomas}
 \affil[13]{Sandia National Laboratories, Org 1442,
 P.O. Box 5800, MS 1320, Albuquerque, NM, 87185-1320,
   \texttt{itomas@sandia.gov}}

\author[*1]{Bruno~Turcksin}
%
\author[14]{David Wells}
\affil[14]{Department of Mathematics, University of North Carolina,
  Chapel Hill, NC 27516, USA.
  {\texttt{drwells@email.unc.edu}}}

\author[15]{Zhuoran Wang}
\affil[15]{Department of Mathematics, Colorado State University, Fort Collins,
          CO 80523-1874, USA.
{\texttt{zhrwang@math.colostate.edu}}}
\renewcommand{\labelitemi}{--}
